Frustration shapes multi-channel Kondo physics: a star graph perspective

### 2023-01-05 manuscript/mscript_mck_full.tex
changed layout to JPCM

\documentclass[superscriptaddress]{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,color,ulem,soul,lipsum}
\usepackage[hidelinks]{hyperref}
\bibliographystyle{apsrev4-1}
\begin{document}

\title{Frustration shapes multi-channel Kondo physics: a star graph perspective}
\author{Siddhartha Patra}
\email{sp14ip022@iiserkol.ac.in }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\author{Abhirup Mukherjee}
\email{am18ip014@iiserkol.ac.in }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\author{Anirban Mukherjee}
\email{mukherjee.anirban.anirban@gmail.com }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
%\affiliation{Ames Laboratory, Ames, Iowa 50011, USA}
\author{N. S. Vidhyadhiraja}
\email{raja@jncasr.ac.in}
\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
\author{A. Taraphder}
\email{arghya@phy.iitkgp.ernet.in}
\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
\author{Siddhartha Lal}
\email{slal@iiserkol.ac.in}
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\date{\today}
\begin{abstract}
	We study the overscreened multi-channel Kondo (MCK) model using the recently developed unitary renormalization group (URG) technique. Our results display the importance of ground state degeneracy in explaining various important properties like the breakdown of screening and the presence of local non-Fermi liquids. The impurity susceptibility of the intermediate coupling fixed point Hamiltonian in the zero-bandwidth (or star graph) limit shows a power-law divergence at low temperature. Despite the absence of inter-channel coupling in the MCK fixed point Hamiltonian, the study of mutual information between any two channels shows non-zero correlation between them. A spectral flow analysis of the star graph reveals that the degenerate ground state manifold possesses topological quantum numbers. Upon disentangling the impurity spin from its partners in the star graph, we find the presence of a local Mott liquid arising from inter-channel scattering processes. The low energy effective Hamiltonian obtained upon adding a finite non-zero conduction bath dispersion to the star graph Hamiltonian for both the two and three-channel cases displays the presence of local non-Fermi liquids arising from inter-channel quantum fluctuations. Specifically, we confirm the presence of a local marginal Fermi liquid in the two channel case, whose properties show logarithmic scaling at low temperature as expected.
Discontinuous behaviour is observed in several measures of ground state entanglement, signalling
the underlying orthogonality catastrophe associated with the degenerate ground state manifold. 
We extend our results to underscreened and perfectly screened MCK models through duality arguments.
A study of channel anisotropy under renormalisation flow reveals a series of quantum phase transitions due to the change in ground state degeneracy. Our work thus presents a template for the study of how a degenerate ground state manifold arising from symmetry and duality properties in a multichannel quantum impurity model can lead to novel multicritical phases at intermediate coupling.

@@

\maketitle

%\tableofcontents

@@

A local antiferromagnetic exchange interaction between a spin-\(\frac{1}{2}\) impurity and its host metal gives rise to the well-understood phenomenon of the Kondo effect (\cite{kondo1964resistance}, see ~\cite{hewson1993} for an extensive discussion). Here, the impurity local moment is screened by the conduction electrons at temperatures below a certain scale called the Kondo temperature~\cite{anderson1969exact,anderson1970exact,anderson1970,wilson1975,andreiKondoreview,
tsvelickKondoreview,affleck1993exact,affleck1995conformal}, leading to a spin singlet ground state and local Fermi liquid excitations above that ground state~\cite{nozieres1974fermi,hewsonp}. The screening manifests as an initial increase at temperatures below the Kondo temperature, followed by a saturation of the resistivity of the metal~\cite{kondo1964resistance,Zhang2013}, and in the saturation of the impurity contribution to the magnetic susceptibility at low temperatures~\cite{wilson1975,andreiKondoreview,tsvelickKondoreview}.
Generalisations of this model are obtained by taking impurities of higher spin~\cite{hewson1993,Noz_blandin_1980,affleck1993exact}, adding interactions between them~\cite{affleck_1992,affleck_ludwig_jones_1992,georges_1999,zarand_chung_2006,
mitchell_logan_2011,mitchell_sela_2012,konig_coleman_2021}, by promoting the model to a lattice of Kondo impurities~\cite{coleman_1987,millis_lee_1987,auerbach_1986,rice_ueda_1986,stewart_1984} or by considering the case of a correlated host metal~\cite{granath_1998}. One can also construct multi-channel Kondo (MCK) models by allowing \(K\) conduction electron channels \( \left(K > 1\right) \) to interact with a spin-\(S_{d}\) impurity~\cite{Noz_blandin_1980,zawadowski_1980,cox_zawadowski_1998} via a common exchange coupling \(\mathcal{J}\). Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the over-screened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type obtained at an intermediate coupling fixed point of the RG flows~\cite{Noz_blandin_1980}. Further, the system displays anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (upon ensuring that temperature is taken to zero {\color{blue} after} the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
This anomalous divergent behaviour is a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: the ground state is susceptible to perturbations that introduce channel anisotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}. This makes the experimental realisation of such states quite challenging.
Nevertheless, several features of the two-channel Kondo model have been reproduced using structural two-level systems~\cite{zawadowski_1980,vladar_1983} interacting with a conduction bath~\cite{cichorek_2005,ralph_buhrman_1992,ralph_ludwig_1994,Iftikhar2015,Zhu2016}.
More recently, it has become possible to tune a two-channel quantum dot system across the quantum phase transition~\cite{Potok2007,Keller2015}, revealing the fractionalisation of the low-energy degrees of freedom~\cite{emery1995,Coleman_tsvelik,mebrahtu_2013}.

The importance of ground state degeneracy and quantum-mechanical frustration in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the quantum criticality and associated non-Fermi liquid physics of the system. This is, at least partially, due to the lack of an intermediate-coupling effective Hamiltonian that describes the low-energy physics of the MCK (i.e., reveals the nature of the excitations). \textit{Frustration} in this context refers to the inability of the impurity spin to bind with the conduction channels, and be screened completely by forming a maximally-entangled singlet ground state. The absence of such frustration in the single-channel spin-1/2 Kondo model (and more generally, the exact screening variant of the MCK) means that imperfect screening \((K \neq 2S_d)\) leads to dramatic differences in the multi-channel models. Indeed, we demonstrate that there exists an orthogonality catastrophe in the imperfectly screened MCK models that leads to the non-Fermi liquid behaviour of its low-energy excitations, and that this is directly related to the existence of a degenerate ground state manifold. The effects of these non-Fermi liquid low energy excitations are expected to appear in measures of many-particle entanglement; the lack of an intermediate coupling Hamiltonian has, however, prevented the study of the renormalisation group (RG) evolution of such measures~\cite{alkurtass_affleck_2016,kim_shim_2021}. 
Importantly, our approach enables a comparison of, for instance, the inter-channel mutual information along the RG flow and as functions of the excitation energies, providing insight into the nature of the fixed point theory.
%}

@@

\section{Fixed point theory of over-screened MCK model}
\label{rg_section}
\subsection{RG flows towards intermediate coupling}
\label{rg_flow_section}
We start with the \(K\)- conduction channel Kondo model Hamiltonian with isotropic couplings \cite{Noz_blandin_1980}:
\begin{gather}
	\label{mc_ham}
	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\alpha^\prime= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~,~~
\end{gather}
where \(\mathcal{J}\) is the Kondo spin-exchange coupling, \(c_{k\alpha,l}\) is the fermionic field operator at momentum \(k\), spin \(\alpha\) and channel \(l\), \(\epsilon_{k,l}\) represents the dispersion of the \(l^\text{th}\) conduction channel, \(\vec \sigma\) is the vector of Pauli matrices and \(\vec S_d = \frac{1}{2}\vec \sigma_d\) is the impurity spin operator. Here, \(l\) sums over the \(K\) channels of the conduction bath, \(k,k^\prime\) sum over all the momentum states of the bath and \(\alpha,\alpha^\prime\) sum over the two spin indices of a single electron.

We now perform a renormalisation group analysis of the MCK Hamiltonian using the recently developed URG method \cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome,1dhubjhep}.
The RG proceeds {by applying unitary transformations in order to block-diagonalize the Hamiltonian by removing number fluctuations of the high energy degrees of freedom}.
At the $j^{th}$ RG step, we focus on decoupling the highest energy electronic state denoted by $\ket{j}$.
%Given the most energetic electronic state at the \(j^\text{th}\) RG step is \(\ket{j}\) and defined by the energy \(D_{(j)}\), 
The Hamiltonian will in general not conserve the number of particles in this state: \(\left[H_{(j)}, \hat n_{j}\right] \neq 0\), and the unitary transformation \(U_{(j)}\) causes this number fluctuation to vanish
%at the next RG step
~\cite{anirbanurg1,anirbanurg2}:
\begin{equation}\begin{aligned}
	H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}~, ~\left[H_{(j-1)}, \hat n_{j}\right] =0~.
\end{aligned}\end{equation}
The unitary transformations are given in terms of a fermionic generator \(\eta_{(j)}\)~\cite{anirbanurg1,anirbanurg2}:
\begin{equation}\begin{aligned}
	\label{unitary}
	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\} = 1~,
\end{aligned}\end{equation}
where \(\left\{\cdot\right\}\) is the anticommutator. Further, $\left[ \eta_{(j)},\eta_{(j)}^\dagger \right] = 2\hat n_{j}-1$. The unitary operator \(U_{(j)}\) mentioned in Eq.~\eqref{unitary} can be thought of as a special case of the most general form \(U = e^\mathcal{S}\) of a unitary operator defined by an anti-Hermitian generator \(\mathcal{S}\). For our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right) \), such that the unitary operator is \(U_{(j)} = e^{\frac{\pi}{4}\left(\eta^\dagger_{(j)} - \eta_{(j)}\right) }\)~\cite{anirbanurg1}. If one then uses the anti-commutation and commutation properties of \(\eta_{(j)},\eta^\dagger_{(j)}\)~\cite{anirbanurg1,anirbanurg2}, the exponential can be expanded in its Taylor series and then resummed into the form in Eq.~\eqref{unitary}.

The generator itself is given by the expression~\cite{anirbanurg1,anirbanurg2}
\begin{equation}\begin{aligned}
	\label{eta_dag}
	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \text{Tr}\left(H_{(j)}c_{j}\right)~.
\end{aligned}\end{equation}
The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space, \(\ket{n_j}\). The presence of the operators in $\eta_{(j)}$ other than $c_j$ are required to ensure that the decoupling of the specific Fock state under consideration is carried out through a unitary modification of the spectrum of the remnant degrees of freedom. Since the \(j^\text{th}\) degree of freedom is coupled with many others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\); this is encoded within the \(\text{Tr}\left(H_{(j)} c_j\right) \) term.
The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms in the Hamiltonian:
\begin{equation}\begin{aligned}
	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)}~.
\end{aligned}\end{equation}
\(H^i_{(j)}\) is that part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does not commute with at least one \(\hat n_l\) for \(l < j\). The RG flow continues till a fixed point is reached at an energy \(D^*\). The Greens function in front of $c_j$ (in Eq.~\ref{eta_dag}) accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).

@@

The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials~\cite{SM}.
On decoupling circular isoenergetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\text{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
\begin{equation}\begin{aligned}
	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{1}{2}\rho {\mathcal{J}}_{(j)} K \right)~, 
\end{aligned}\end{equation}
where \(\mathcal{N}_{(j)}\) is the number of electronic states at the energy shell \(D_{(j)}\). We work in the low quantum fluctuation regime \(\omega_{(j)} < \frac{D_{(j)}}{2}\). There are three fixed points of the RG equation. One arises from the vanishing of the denominator, and was present in the single-channel Kondo RG equation as well \cite{kondo_urg}. As shown there, this fixed-point goes to \({\mathcal{J}}^* = \infty\) as the bare bandwidth of the conduction electrons is made large. The other fixed point is the trivial one at \({\mathcal{J}}^* = 0\). The third fixed point is reached when the numerator vanishes: \({\mathcal{J}}^* = \frac{2}{K \rho}\) \cite{Gan_mchannel_1994,Kogan_2018,Kuramoto1998,Noz_blandin_1980}. Only the intermediate fixed point is found to be stable. This is consistent with results from Bethe ansatz calculations~\cite{Tsvelick_Weigmann_mchannel_1984,andrei_destri_1984,zarand_costi_2002,andrei_jerez_1995,Tsvelick_1985,Tsvelick1984}, CFT calculations~\cite{affleck_1991_overscreen,affleck1993exact,affleck_ludwig_1991}, bosonization treatments~\cite{emery_kivelson,vondelft_prl_1998} and NRG analysis~\cite{pang_cox_1991,mitchell_bulla_2014}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.45\textwidth]{rgflow.pdf}
	\caption{The three fixed points of the over-screened RG equation. Only the intermediate one is stable.}
	\label{rg_flow}
\end{figure}

@@

\subsection{The star graph as the zero-bandwidth limit of the fixed point Hamiltonian}
\label{sec:star graph}
The fixed point Hamiltonian takes the form
\begin{equation}\begin{aligned}
	H^* = \sum_l\left[ \sum^*_{k}\epsilon_{k,l} \hat n_{k\alpha,l} + {\mathcal{J}}\sum_{kk^\prime\atop{\alpha,\alpha^\prime}}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\right]~.
\end{aligned}\end{equation}
We have not explicitly written the decoupled degrees of freedom \(D_{(j)} > D^*\) in the Hamiltonian. The \(*\) over the summations indicate that only the momenta inside the window \(D^*\) enter the summation.

>>>>

\documentclass{iopart}
\usepackage{iopams}  
\usepackage{braket,graphicx,amsmath,hyperref}
\bibliographystyle{unsrt}
\begin{document}

\title{Frustration shapes multi-channel Kondo physics: a star graph perspective}
\author{Siddhartha Patra$^1$, Abhirup Mukherjee$^1$, Anirban Mukherjee$^1$, N. S. Vidhyadhiraja$^4$, A. Taraphder$^5$ and Siddhartha Lal$^1$}
\eads{\mailto{sp14ip022@iiserkol.ac.in}, \mailto{am18ip014@iiserkol.ac.in}, \mailto{mukherjee.anirban.anirban@gmail.com}, \mailto{raja@jncasr.ac.in}, \mailto{arghya@phy.iitkgp.ernet.in}, \mailto{slal@iiserkol.ac.in}}

\address{$^1$Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}

\address{$^4$Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}

\address{$^5$Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}

\date{\today}

\begin{abstract}
	We study the overscreened multi-channel Kondo (MCK) model using the recently developed unitary renormalization group (URG) technique. Our results display the importance of ground state degeneracy in explaining various important properties like the breakdown of screening and the presence of local non-Fermi liquids. The impurity susceptibility of the intermediate coupling fixed point Hamiltonian in the zero-bandwidth (or star graph) limit shows a power-law divergence at low temperature. Despite the absence of inter-channel coupling in the MCK fixed point Hamiltonian, the study of mutual information between any two channels shows non-zero correlation between them. A spectral flow analysis of the star graph reveals that the degenerate ground state manifold possesses topological quantum numbers. Upon disentangling the impurity spin from its partners in the star graph, we find the presence of a local Mott liquid arising from inter-channel scattering processes. The low energy effective Hamiltonian obtained upon adding a finite non-zero conduction bath dispersion to the star graph Hamiltonian for both the two and three-channel cases displays the presence of local non-Fermi liquids arising from inter-channel quantum fluctuations. Specifically, we confirm the presence of a local marginal Fermi liquid in the two channel case, whose properties show logarithmic scaling at low temperature as expected.
Discontinuous behaviour is observed in several measures of ground state entanglement, signalling
the underlying orthogonality catastrophe associated with the degenerate ground state manifold. 
We extend our results to underscreened and perfectly screened MCK models through duality arguments.
A study of channel anisotropy under renormalisation flow reveals a series of quantum phase transitions due to the change in ground state degeneracy. Our work thus presents a template for the study of how a degenerate ground state manifold arising from symmetry and duality properties in a multichannel quantum impurity model can lead to novel multicritical phases at intermediate coupling.

@@

% \maketitle

\ioptwocol

@@

A local antiferromagnetic exchange interaction between a spin-\(\frac{1}{2}\) impurity and its host metal gives rise to the well-understood phenomenon of the Kondo effect (\cite{kondo1964resistance}, see ~\cite{hewson1993} for an extensive discussion). Here, the impurity local moment is screened by the conduction electrons at temperatures below a certain scale called the Kondo temperature~\cite{anderson1969exact,anderson1970exact,anderson1970,wilson1975,andreiKondoreview,
tsvelickKondoreview,affleck1993exact,affleck1995conformal}, leading to a spin singlet ground state and local Fermi liquid excitations above that ground state~\cite{nozieres1974fermi,hewsonp}. The screening manifests as an initial increase at temperatures below the Kondo temperature, followed by a saturation of the resistivity of the metal~\cite{kondo1964resistance,Zhang2013}, and in the saturation of the impurity contribution to the magnetic susceptibility at low temperatures~\cite{wilson1975,andreiKondoreview,tsvelickKondoreview}.
Generalisations of this model are obtained by taking impurities of higher spin~\cite{hewson1993,Noz_blandin_1980,affleck1993exact}, adding interactions between them~\cite{affleck_1992,affleck_ludwig_jones_1992,georges_1999,zarand_chung_2006,
mitchell_logan_2011,mitchell_sela_2012,konig_coleman_2021}, by promoting the model to a lattice of Kondo impurities~\cite{coleman_1987,millis_lee_1987,auerbach_1986,rice_ueda_1986,stewart_1984} or by considering the case of a correlated host metal~\cite{granath_1998}. One can also construct multi-channel Kondo (MCK) models by allowing \(K\) conduction electron channels \( \left(K > 1\right) \) to interact with a spin-\(S_{d}\) impurity~\cite{Noz_blandin_1980,zawadowski_1980,cox_zawadowski_1998} via a common exchange coupling \(\mathcal{J}\). Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the over-screened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type obtained at an intermediate coupling fixed point of the RG flows~\cite{Noz_blandin_1980}. Further, the system displays anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (upon ensuring that temperature is taken to zero after the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
This anomalous divergent behaviour is a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: the ground state is susceptible to perturbations that introduce channel anisotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}. This makes the experimental realisation of such states quite challenging.
Nevertheless, several features of the two-channel Kondo model have been reproduced using structural two-level systems~\cite{zawadowski_1980,vladar_1983} interacting with a conduction bath~\cite{cichorek_2005,ralph_buhrman_1992,ralph_ludwig_1994,Iftikhar2015,Zhu2016}.
More recently, it has become possible to tune a two-channel quantum dot system across the quantum phase transition~\cite{Potok2007,Keller2015}, revealing the fractionalisation of the low-energy degrees of freedom~\cite{emery1995,Coleman_tsvelik,mebrahtu_2013}.

The importance of ground state degeneracy and quantum-mechanical \textit{frustration} in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the quantum criticality and associated non-Fermi liquid physics of the system. This is, at least partially, due to the lack of an intermediate-coupling effective Hamiltonian that describes the low-energy physics of the MCK (i.e., reveals the nature of the excitations). Frustration in this context refers to the inability of the impurity spin to bind with the conduction channels, and be screened completely by forming a maximally-entangled singlet ground state. The absence of such frustration in the single-channel spin-1/2 Kondo model (and more generally, the exact screening variant of the MCK) means that imperfect screening \((K \neq 2S_d)\) leads to dramatic differences in the multi-channel models. Indeed, we demonstrate that there exists an orthogonality catastrophe in the imperfectly screened MCK models that leads to the non-Fermi liquid behaviour of its low-energy excitations, and that this is directly related to the existence of a degenerate ground state manifold. The effects of these non-Fermi liquid low energy excitations are expected to appear in measures of many-particle entanglement; the lack of an intermediate coupling Hamiltonian has, however, prevented the study of the renormalisation group (RG) evolution of such measures~\cite{alkurtass_affleck_2016,kim_shim_2021}. 
Importantly, our approach enables a comparison of, for instance, the inter-channel mutual information along the RG flow and as functions of the excitation energies, providing insight into the nature of the fixed point theory.
%}

@@

\section{Fixed point theory of over-screened MCK model}
\label{rg_section}
\subsection{RG flows towards intermediate coupling}
\label{rg_flow_section}
We start with the \(K\)- conduction channel Kondo model Hamiltonian with isotropic couplings \cite{Noz_blandin_1980}:
\begin{eqnarray}
	\label{mc_ham}
	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\alpha^\prime= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~,~~
\end{eqnarray}
where \(\mathcal{J}\) is the Kondo spin-exchange coupling, \(c_{k\alpha,l}\) is the fermionic field operator at momentum \(k\), spin \(\alpha\) and channel \(l\), \(\epsilon_{k,l}\) represents the dispersion of the \(l^\mathrm{th}\) conduction channel, \(\vec \sigma\) is the vector of Pauli matrices and \(\vec S_d = \frac{1}{2}\vec \sigma_d\) is the impurity spin operator. Here, \(l\) sums over the \(K\) channels of the conduction bath, \(k,k^\prime\) sum over all the momentum states of the bath and \(\alpha,\alpha^\prime\) sum over the two spin indices of a single electron.

We now perform a renormalisation group analysis of the MCK Hamiltonian using the recently developed URG method \cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome,1dhubjhep}.
The RG proceeds {by applying unitary transformations in order to block-diagonalize the Hamiltonian by removing number fluctuations of the high energy degrees of freedom}.
At the $j^{th}$ RG step, we focus on decoupling the highest energy electronic state denoted by $\ket{j}$.
%Given the most energetic electronic state at the \(j^\mathrm{th}\) RG step is \(\ket{j}\) and defined by the energy \(D_{(j)}\), 
The Hamiltonian will in general not conserve the number of particles in this state: \(\left[H_{(j)}, \hat n_{j}\right] \neq 0\), and the unitary transformation \(U_{(j)}\) causes this number fluctuation to vanish
%at the next RG step
~\cite{anirbanurg1,anirbanurg2}:
\begin{eqnarray}
	H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}~, ~\left[H_{(j-1)}, \hat n_{j}\right] =0~.
\end{eqnarray}
The unitary transformations are given in terms of a fermionic generator \(\eta_{(j)}\)~\cite{anirbanurg1,anirbanurg2}:
\begin{eqnarray}
	\label{unitary}
	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\} = 1~,
\end{eqnarray}
where \(\left\{\cdot\right\}\) is the anticommutator. Further, $\left[ \eta_{(j)},\eta_{(j)}^\dagger \right] = 2\hat n_{j}-1$. The unitary operator \(U_{(j)}\) mentioned in Eq.~\eqref{unitary} can be thought of as a special case of the most general form \(U = e^\mathcal{S}\) of a unitary operator defined by an anti-Hermitian generator \(\mathcal{S}\). For our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right) \), such that the unitary operator is \(U_{(j)} = e^{\frac{\pi}{4}\left(\eta^\dagger_{(j)} - \eta_{(j)}\right) }\)~\cite{anirbanurg1}. If one then uses the anti-commutation and commutation properties of \(\eta_{(j)},\eta^\dagger_{(j)}\)~\cite{anirbanurg1,anirbanurg2}, the exponential can be expanded in its Taylor series and then resummed into the form in Eq.~\eqref{unitary}.

The generator itself is given by ~\cite{anirbanurg1,anirbanurg2}
\begin{eqnarray}
	\label{eta_dag}
	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \mathrm{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \mathrm{Tr}\left(H_{(j)}c_{j}\right)~.
\end{eqnarray}
The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space, \(\ket{n_j}\). The presence of the operators in $\eta_{(j)}$ other than $c_j$ are required to ensure that the decoupling of the specific Fock state under consideration is carried out through a unitary modification of the spectrum of the remnant degrees of freedom. Since the \(j^\mathrm{th}\) degree of freedom is coupled with many others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\); this is encoded within the \(\mathrm{Tr}\left(H_{(j)} c_j\right) \) term.
The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms in the Hamiltonian:
\begin{eqnarray}
	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)}~.
\end{eqnarray}
\(H^i_{(j)}\) is that part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does not commute with at least one \(\hat n_l\) for \(l < j\). The RG flow continues till a fixed point is reached at an energy \(D^*\). The Greens function in front of $c_j$ (in Eq.~\ref{eta_dag}) accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\mathrm{Tr}\left( H_{(j)}\hat n_j \right) \).

@@

The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials~\cite{SM}.
On decoupling circular isoenergetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\mathrm{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
\begin{eqnarray}
	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{1}{2}\rho {\mathcal{J}}_{(j)} K \right)~, 
\end{eqnarray}
where \(\mathcal{N}_{(j)}\) is the number of electronic states at the energy shell \(D_{(j)}\). We work in the low quantum fluctuation regime \(\omega_{(j)} < \frac{D_{(j)}}{2}\). There are three fixed points of the RG equation. One arises from the vanishing of the denominator, and was present in the single-channel Kondo RG equation as well \cite{kondo_urg}. As shown there, this fixed-point goes to \({\mathcal{J}}^* = \infty\) as the bare bandwidth of the conduction electrons is made large. The other fixed point is the trivial one at \({\mathcal{J}}^* = 0\). The third fixed point is reached when the numerator vanishes: \({\mathcal{J}}^* = \frac{2}{K \rho}\) \cite{Gan_mchannel_1994,Kogan_2018,Kuramoto1998,Noz_blandin_1980}. Only the intermediate fixed point is found to be stable. This is consistent with results from Bethe ansatz calculations~\cite{Tsvelick_Weigmann_mchannel_1984,andrei_destri_1984,zarand_costi_2002,andrei_jerez_1995,Tsvelick_1985,Tsvelick1984}, CFT calculations~\cite{affleck_1991_overscreen,affleck1993exact,affleck_ludwig_1991}, bosonization treatments~\cite{emery_kivelson,vondelft_prl_1998} and NRG analysis~\cite{pang_cox_1991,mitchell_bulla_2014}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.45\textwidth]{rgflow.pdf}
	\caption{The three fixed points of the over-screened RG equation. Only the intermediate one is stable.}
	\label{rg_flow}
\end{figure}

@@

\subsection{The star graph as the zero-bandwidth limit of the fixed point Hamiltonian}
\label{sec:star graph}
The fixed point Hamiltonian takes the form
\begin{eqnarray}
	H^* = \sum_l\left[ \sum^*_{k}\epsilon_{k,l} \hat n_{k\alpha,l} + {\mathcal{J}}\sum_{kk^\prime\atop{\alpha,\alpha^\prime}}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\right].~ ~ ~ ~
\end{eqnarray}
We have not explicitly written the decoupled degrees of freedom \(D_{(j)} > D^*\) in the Hamiltonian. The \(*\) over the summations indicate that only the momenta inside the window \(D^*\) enter the summation.
